\documentclass[letter,10pt]{article}
\usepackage[utf8]{inputenc}

%====================
% File:         resume.tex
% Editor:       https://github.com/TimmyChan 
%               https://www.linkedin.com/in/timmy-l-chan/
% Last Updated: Jan 7th, 2022
% Notes:        All formatting is done in TLCresume.sty
%               No need to touch that file. 
%               All actual content is in the sections/ folder.
%====================

\usepackage{../shared_resources/TLCresume}

%====================
% CONTACT INFORMATION
%====================
\def\name{Colin Middleton} % Name Here
\def\phone{+1-360-206-7812}
\def\city{Leavenworth, WA}
\def\email{colindmiddleton@gmail.com}
\def\LinkedIn{colin-middleton-000} % linkedin.com/in/______
\def\github{middlec000} % github username
\def\role{Entry Level Data Scientist} % JOB TITLE
\def\web{https://middlec000.github.io/} % website

\input{../shared_resources/header}
\begin{document}
%====================
% Objective Statement
%====================
Recent Eastern Washington University graduate with an MS in Applied Mathematics. Completed thesis project on predicting likelihood of homelessness based on an individual's utility billing history. Strong background in applied mathematics and statistics with practical experience in data exploration, manipulation, analysis, and prediction. Seeking to launch career with innovative and learning-focused company.

\section{Skills}
\begin{tabular}{p{11em} p{1em} p{43em}}
    \skills{Software Languages} & & Python (pandas, numpy, statsmodels, scikit-learn, matplotlib, seaborn, scipy, tensorflow, streamlit), \\
     & & R, SQL, Java, Git, \LaTeX, Markdown \\
     \skills{Software Tools} & & Visual Studio Code, Anaconda, Jupyter Notebooks, Excel, Power BI \\
    \skills{Data Analysis} & & Correlation, Box plot, Histogram, Q-Q Plot, Hypothesis Testing \\
    \skills{Data Preparation} & & Reformatting, Filtering, Imputation, Class Balancing \\
    \skills{Supervised Learning} & & Linear Regression, Logistic Regression, Cox Proportional Hazards, Vanilla ANN, LSTM, Decision Trees \\
    \skills{Unsupervised Learning} & & K-Means Clustering, Hierarchical Clustering, Principal Component Analysis \\
    \skills{Performance Analysis} & & Performance Metrics, Parameter Interpretation
\end{tabular}

\section{Education}
\subsection{{Master of Science in Applied Mathematics  \hfill September 2019 --- June 2021}}
\subtext{Eastern Washington University \hfill Cheney, WA}
\begin{zitemize}
    \item GPA: 4.0
    \item First graduate of reopened program (2021)
    \item Outstanding Graduate Award (2021)
    \item Graduate Service Appointment (2020 - 2021)
\end{zitemize}

\subsection{{Bachelor of Science in Mathematics \hfill September 2013 --- December 2017}}
\subtext{Western Washington University \hfill Bellingham, WA}
\begin{zitemize}
    \item GPA: 3.5
    \item Minors: Chemistry
    \item Honors Program Graduate
    \item Math Fellow (2015 - 2017)
    \item Presidential Scholarship (2013)
\end{zitemize}

\section{Project Experience}
\subsection{{Data Analyst / The Wordler \hfill March 2022 --- Present}}
\subtext{Personal Project \hfill Leavenworth, WA}
\begin{zitemize}
    \item Acquired list of words from Wordle website source code and word frequencies from Kaggle dataset.
    \item Built 6 component data filter using regular expressions in Python.
    \item Published user-friendly Streamlit website to suggest Wordle words for users.
    \item Words sorted and displayed by user preference: Word Frequency, Letter Frequency, Letter Position Frequency.
    \item \url{https://share.streamlit.io/middlec000/wordler/main/src/main.py}
\end{zitemize}

\subsection{{Software Engineer / Grades vs Student Characteristic \hfill December 2021}}
\subtext{Personal Project \hfill Alpine, WY}
\begin{zitemize}
    \item Published a User-friendly Streamlit web interface where users can use an example dataset or upload data.
    \item Website uses an ANOVA test to determine if there is a significant difference in grades between groups of students with groups from chosen characteristic such as race or neighborhood.
    \item Automatically performs normality and skedasticity hypothesis tests and informs user of results.
    \item \url{https://github.com/middlec000/grades_vs_student_characteristic}
\end{zitemize}

\newpage
\subsection{{Data Science Lead / Homelessness Prediction \hfill June 2020 --- June 2021}}
\subtext{Spokane Predictive Analytics and Master's Thesis Project \hfill Spokane, WA}
\begin{zitemize}
    \item Received, matched on composite key, and preprocessed 4,785,131 rows of de-identified data from 8 csv files.
    \item Communicated with data providers to improve datasets over 5 iterations.
    \item Performed exploratory data analysis on the monthly billing data representing 91,591 people over a 5-year period using visualization techniques and 4 types of correlation to discover relationships and trends.
    \item Established data homogeneity across years using ranks of variable-outcome correlations.
    \item Engineered 2 new cumulative features and 3 new aggregate features.
    \item Investigated longitudinal prediction approaches using Linear Regression, Cox Proportional Hazards, and LSTM models.
    \item Investigated non-longitudinal prediction approaches using Logistic Regression and Vanilla ANN models.
    \item Evaluated and compared models based on Receiver Operator Characteristic curves and Area Under the Curve. The Logistic Regression model performed best with an AUC of 0.81 - similar to current research that incorporated richer data sources.
    \item Implemented K-Folds and minority class oversampling to make model performance more reproducible and combat extreme class imbalance - only 0.39\% of cases were of the positive class.
    \item Presented findings to the City Council of Spokane and defended as master's thesis.
    \item Paper pending publication in a peer reviewed journal.
    \item \url{https://github.com/middlec000/SPA_predict_homelessness}
\end{zitemize}

\subsection{{Software Engineer / Academic Paper Clustering by Topic \hfill January 2021 --- March 2021}}
\subtext{Big Data Analytics Class Project, Eastern Washington University \hfill Spokane, WA}
\begin{zitemize}
    \item Established a data preprocessing pipeline that pulled the body of each paper, detected the language - retaining only English documents, tokenized and lemmatized each text, then converted all documents to sparse vectors of TF-IDF scores using Python.
    \item Assisted with development of a customized K-Means algorithm optimized for sparse, largely disjoint TF-IDF vectors.
    \item Developed component to find the number of clusters to form using the Elbow Method.
    \item Currently developing a fast hierarchical text document clustering Python package as an extension of this work.
    \item \url{https://github.com/middlec000/fhdc}
\end{zitemize}

\subsection{{Data Scientist / Traffic Prediction \hfill January 2017 --- December 2017}}
\subtext{Whatcom Council of Governments and Senior Project, Western Washington University \hfill Bellingham, WA}
\begin{zitemize}
    \item Predicted traffic flow arriving at the Peace Arch and Blaine US / Canadian border crossings based on upflow traffic sensors using averaging, Principal Component Analysis, and curve fitting methods.
    \item Presented findings to Whatcom Council of Governments and Western Washington University faculty.
\end{zitemize}

\section{Work Experience}
\subsection{{Architectural Drafter \hfill January 2022 --- Present}}
\subtext{Alison Miller Architect \hfill Leavenworth, WA}
\begin{zitemize}
    \item Create architectural drawings using AutoCAD LT: floor plans, roof plans, sections, exterior elevations, window and door schedules.
    \item Assemble drawing sheet set: dimensions, code compliance, viewport setup.
    \item Communicate work schedule and technical project details.
    \item Site measure existing buildings for remodel.
    \item Managed and shared files with Dropbox.
\end{zitemize}

\subsection{{Architectural Drafter \hfill October 2018 --- December 2021}}
\subtext{Brooks Middleton Architect \hfill Anacortes, WA}
\begin{zitemize}
    \item Created drawings using AutoCAD LT: site plans, floor plans, roof plans, electrical plans, sections, interior elevations, exterior elevations, window, door, and finish schedules.
    \item Communicated work schedule and technical project details.
    \item Provided feedback and suggestions on design.
    \item Researched building code and construction product specifications.
\end{zitemize}

\newpage
\subsection{{Graduate Service Appointment \hfill September 2020 --- June 2021}}
\subtext{Eastern Washington University \hfill Cheney, WA}
\begin{zitemize}
    \item Trained as a university level mathematics teacher.
    \item Completed a final project on making lessons more applicable to the lives of the students by incorporating familiar contexts into mathematical situations.
    \item Developed 1 lesson plan and taught 2 live remote class sessions (linear algebra).
    \item Graded homework and exams fairly and systematically.
    \item Provided feedback and suggestions to students about assignments.
    \item Provided feedback to professors about students' comprehension of class material.
\end{zitemize}

\subsection{{Teacher Assistant \hfill September 2019 --- September 2020}}
\subtext{Eastern Washington University \hfill Cheney, WA}
\begin{zitemize}
    \item Graded homework and exams fairly and systematically.
    \item Provided feedback and suggestions to students about assignments.
    \item Provided feedback to professors about students' comprehension of class material.
\end{zitemize}

\subsection{{Architectural Drafter \hfill November 2018 --- May 2019}}
\subtext{Beacon Rock Architecture Group \hfill La Center, WA}
\begin{zitemize}
    \item Created drawings using AutoCAD LT: floor plans, roof plans, sections, exterior elevations, window and door schedules.
    \item Communicated work schedule and technical project details.
    \item Researched building code.
    \item Managed and shared files with Dropbox.
\end{zitemize}

\subsection{{R \& D Intern / Liquid Gas Mixing System \hfill July 2016 --- August 2016}}
\subtext{ESS Inc. \hfill Portland, OR}
\begin{zitemize}
    \item Assisted with preparation and maintenance of battery testing stations.
    \item Assisted with fabrication and improvement of liquid-gas mixing system, component of large scale battery.
\end{zitemize}


\section{Publications}
\subsection{Prediction of first-time homelessness risk based on utility
payment history \hfill Pending}
\subtext{Eastern Washington University \hfill Cheney, WA}
\begin{zitemize}
    \item Advisor: Dr. Andrew Oster, Associate Professor, Eastern Washington University.
    \item Paper based on Homelessness Prediction project with Spokane Predictive Analytics - see projects.
\end{zitemize}


\section{Related Coursework}
\subsection{{Eastern Washington University \hfill September 2019 --- June 2021}}
\begin{zitemize}
    \item Big Data Analytics (A)
    \item Advanced Topics in Statistics (A)
    \item Applied Linear Statistical Modeling (A)
    \item Data Mining (A)
    \item Independent Study: Time Series Analysis (A)
    \item Relational Database Systems (A)
    \item Data Structures (A)
\end{zitemize}

\subsection{{Western Washington University \hfill September 2013 --- December 2017}}
\begin{zitemize}
    \item Probability and Statistical Inference (A)
    \item Nonlinear Optimization (B+)
    \item Linear Optimization (B-)
    \item Linear Algebra (A-)
    \item Mathematical Modeling (A)
\end{zitemize}

\end{document}